Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-06-02 R0V0.tex
Separate the Riemannian energy and add a log-scale figure

\mypara Figure~\ref{fig:3dsim} shows simulations of the network~\eqref{eq:example} composed of four systems with the network structure as represented by the graph in Figure~\ref{fig:graph} under different inputs, and the Riemannian metric $V$. Note that, when random initial random initial conditions are considered, the system may diverge from the neighborhood of the origin.

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\linewidth]{./imgs/simulation.eps}
	\vspace{-2em}
	\caption{Simulation of network~\eqref{eq:example} with the target trajectory being the origin and under the controller obtained according to different constrains for the computation of $Y$: diagonal, neighbour and unconstrained. In contrast to these, the open loop simulation (performed with $u\equiv0$) does not converge to the origin. The bottom graph shows the variation of the Riemannian metric along the solutions of each case.}
	\label{fig:3dsim}
\end{figure}

>>>>

\mypara Figure~\ref{fig:3dsim} shows simulations of the network~\eqref{eq:example} composed of four systems with the network structure as represented by the graph in Figure~\ref{fig:graph} under different inputs. Figure~\ref{fig:Riemannian energy} show the Riemannian metric $V$ computed along solutions to network~\eqref{eq:example}. Note that, when random initial random initial conditions are considered, the system may diverge from the neighborhood of the origin.

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\linewidth]{./imgs/simulation.eps}

	\caption{Simulation of network~\eqref{eq:example} with the target trajectory being the origin and under the controller obtained according to different constrains for the computation of $Y$: diagonal, neighbour and unconstrained. In contrast to these, the open loop simulation (performed with $u\equiv0$) does not converge to the origin.}
	\label{fig:3dsim}
\end{figure}

\begin{figure}[htbp!]
	\centering
%	\includegraphics[]{}
	\includegraphics[width=\linewidth]{./imgs/Riemannian_energy.eps}
	\caption{Computation of the Riemannian energy along solutions to \eqref{eq:example}, according to each of each case. The bottom graph is the logarithm of the Riemannian energy.}
	\label{fig:Riemannian energy}
\end{figure}
